Descriptive analysis 2

### 2022-08-12 03_analysis/Analysis_description.Rmd
Add files via upload

@@

od_aid_average$rank_aid <- rank(-od_aid_average$mean_of_aid, ties.method = "max")
od_aid_average
```
Iraq gets the most aids (aids from humanitarian aids)

@@

Russia has most debts, but no aids; Iraq has most aids, but no debts at all.

>>>>

# and load Miles' file: new_dt
```

```{r}
unique(new_dt$recipient)
#142
```

@@

od_aid_average$rank_aid <- rank(-od_aid_average$mean_of_aid, ties.method = "max")
od_aid_average
```
Iraq gets the most aids (aids from humanitarian aids), with a surge in 2010 and 2014.

@@

Russia has most debts, but no aids; Iraq has most aids, but no debts at all. (China-Iraq: https://www.mei.edu/publications/china-iraq-relations-poised-quantum-leap#_ftn39)
